Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-10-25 psy_peds_3.Rmd
code added to save the output aggregate counts

clinical_filtered <- clinical_raw %>%
  filter( len_hospitalisation > min_hosp_days, 
          cohort  %in% c("AllAdm")) %>%
  dplyr::mutate( date = as.Date( calendar_date, format = dateFormat ),
                 weeks = as.Date(cut( date, breaks = "week")),
                 month = as.Date(cut( date, breaks = "month")),
                 year = format( date, "%Y"), 
                 period = ifelse( date < pandemic_start_date,
                                  "before_pandemic", "during_pandemic"))

@@

```{r}
stopifnot(unique(all_codes$cohort) == "AllAdm")
stopifnot(unique(all_codes$in_hospital) == 1)
stopifnot(unique(all_codes$len_hospitalisation > min_hosp_days))
stopifnot(nrow(all_codes) == nrow(observation_table))
stopifnot(length(unique(all_codes$patient_num)) == length(unique(demographic_table$patient_num)))
stopifnot(length(unique(all_codes$patient_num)) == length(unique(observation_table$patient_num)))
stopifnot(length(unique(all_codes$patient_num)) == length(unique(clinical_table$patient_num)))
stopifnot(nrow(distinct(all_codes, patient_num, n_hospitalisation)) == nrow(distinct(clinical_table, patient_num, n_hospitalisation)))
stopifnot(nrow(distinct(all_codes, patient_num, days_since_admission)) == nrow(distinct(observation_table, patient_num, days_since_admission)))
```

@@

```{r}
stopifnot(unique(all_codes_ado$cohort) == "AllAdm")
stopifnot(unique(all_codes_ado$in_hospital) == 1)
stopifnot(unique(all_codes_ado$len_hospitalisation > min_hosp_days))
stopifnot(nrow(all_codes_ado) == nrow(observation_table_ado))
stopifnot(length(unique(all_codes_ado$patient_num)) == length(unique(demographic_table_ado$patient_num)))
stopifnot(length(unique(all_codes_ado$patient_num)) == length(unique(observation_table_ado$patient_num)))
stopifnot(length(unique(all_codes_ado$patient_num)) == length(unique(clinical_table_ado$patient_num)))
stopifnot(nrow(distinct(all_codes_ado, patient_num, n_hospitalisation)) == nrow(distinct(clinical_table_ado, patient_num, n_hospitalisation)))
stopifnot(nrow(distinct(all_codes_ado, patient_num, days_since_admission)) == nrow(distinct(observation_table_ado, patient_num, days_since_admission)))
```

@@

# ggplot(bootstrapped_fitted_df, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
#   geom_line(aes(color = period),
#             alpha = 0.03) +
#   geom_line(data = quantile_bootstrapped_fitted,
#             aes(y = value, group = interaction(quantiles, period)),
#             linetype = "dashed") +
#   geom_line(data = quantile_bootstrapped_fitted[quantile_bootstrapped_fitted$quantiles == "50%", ],
#             aes(y = value, group = period)) +
#   geom_point(data = patient_count_psy_period_psy,
#              aes(y = percentage),
#              alpha = 0.5) +
#   scale_colour_manual(values = cbPalette) +
#   guides(color = guide_legend(override.aes = list(alpha = 1))) +
#   annotate("text",
#            x = as.Date("2019-10-01"),
#            y = max(patient_count_psy_period_psy[["percentage"]]) + 5,
#            label = annotation) +
#   labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
#        subtitle = "Parametric bootstrap estimation: (1000 iterations)",
#        x = "Calendar dates",
#        y = "Percentage",
#        color = "Period")

@@

# Save the output in a RData file. 
```{r}
#length_hospitalisation_values <- input_data %>% 
#  dplyr::distinct( patient_num, n_hospitalisation, len_hospitalisation ) %>%
#  dplyr::mutate( siteid = site ) %>%
#  dplyr::select( len_hospitalisation, siteid )
save( count_icd,
      patient_count_psy_period_psy,
      patient_count_psy_period_psy_clear,
      bootstrapped_coefficients_df,
      bootstrapped_fitted_df,
      perc_disorder_group,
      patients_hospitalized_agg_sex_perc,
      table1,
#      length_hospitalisation_values,
#      obs_by_day,
      file = paste0("output/peds_psy_aggResults_", unique(as.character(demo_raw$siteid)), ".RData"))
```

>>>>

clinical_filtered <- clinical_raw %>%
  filter( len_hospitalisation >= min_hosp_days, 
          cohort  %in% c("AllAdm")) %>%
  dplyr::mutate( date = as.Date( calendar_date, format = dateFormat ),
                 weeks = as.Date(cut( date, breaks = "week")),
                 month = as.Date(cut( date, breaks = "month")),
                 year = format( date, "%Y"), 
                 period = ifelse( date < pandemic_start_date,
                                  "before_pandemic", "during_pandemic"))

@@

```{r}
stopifnot(unique(all_codes$cohort) == "AllAdm")
stopifnot(unique(all_codes$in_hospital) == 1)
stopifnot(unique(all_codes$len_hospitalisation >= min_hosp_days))
stopifnot(nrow(all_codes) == nrow(observation_table))
stopifnot(length(unique(all_codes$patient_num)) == length(unique(demographic_table$patient_num)))
stopifnot(length(unique(all_codes$patient_num)) == length(unique(observation_table$patient_num)))
stopifnot(length(unique(all_codes$patient_num)) == length(unique(clinical_table$patient_num)))
stopifnot(nrow(distinct(all_codes, patient_num, n_hospitalisation)) == nrow(distinct(clinical_table, patient_num, n_hospitalisation)))
stopifnot(nrow(distinct(all_codes, patient_num, days_since_admission)) == nrow(distinct(observation_table, patient_num, days_since_admission)))
```

@@

```{r}
stopifnot(unique(all_codes_ado$cohort) == "AllAdm")
stopifnot(unique(all_codes_ado$in_hospital) == 1)
stopifnot(unique(all_codes_ado$len_hospitalisation >= min_hosp_days))
stopifnot(nrow(all_codes_ado) == nrow(observation_table_ado))
stopifnot(length(unique(all_codes_ado$patient_num)) == length(unique(demographic_table_ado$patient_num)))
stopifnot(length(unique(all_codes_ado$patient_num)) == length(unique(observation_table_ado$patient_num)))
stopifnot(length(unique(all_codes_ado$patient_num)) == length(unique(clinical_table_ado$patient_num)))
stopifnot(nrow(distinct(all_codes_ado, patient_num, n_hospitalisation)) == nrow(distinct(clinical_table_ado, patient_num, n_hospitalisation)))
stopifnot(nrow(distinct(all_codes_ado, patient_num, days_since_admission)) == nrow(distinct(observation_table_ado, patient_num, days_since_admission)))
```

@@

ggplot(bootstrapped_fitted_df, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted[quantile_bootstrapped_fitted$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy,
             aes(y = percentage),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  annotate("text",
           x = as.Date("2019-10-01"),
           y = max(patient_count_psy_period_psy[["percentage"]]) + 5,
           label = plot_annotation) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period")

@@

# Save the output in a RData file. 
```{r}
length_hospitalisation_values <- all_codes_psy %>% 
  dplyr::distinct( patient_num, n_hospitalisation, len_hospitalisation, period ) %>%
  dplyr::mutate( siteid = site ) %>%
  dplyr::select( len_hospitalisation, siteid, period )

# add the site id as column for each of the output data frames
count_icd$siteid = site 
patient_count_psy_period_psy$siteid = site 
patient_count_psy_period_psy_clear$siteid = site 
bootstrapped_coefficients_df$siteid = site 
bootstrapped_fitted_df$siteid = site 
perc_disorder_group$siteid = site 
patients_hospitalized_agg_sex_perc$siteid = site 
table1$siteid = site

save( count_icd,
      patient_count_psy_period_psy,
      patient_count_psy_period_psy_clear,
      bootstrapped_coefficients_df,
      bootstrapped_fitted_df,
      perc_disorder_group,
      patients_hospitalized_agg_sex_perc,
      table1,
      length_hospitalisation_values,
      file = paste0("output/peds_psy_aggResults_", site, ".RData"))
```
